Untitled

### 2024-11-19 code/manuscript_altanalysis.Rmd
Better Stratified Figure

strat.temp <- (cbind(core.did.estimates.strat[,1], strat.temp[-1,c(1:2)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "First Shock"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)] %>% 
  rbind((cbind(core.did.estimates.strat[,1], strat.temp[-1,c(5:6)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)])

strat.temp %>% 
  mutate(Measure = ifelse(Outcome %in% c("Qcomp","Total","Altman","logPatsPerStaff","Staff","Closed"), "Overall Metrics", 
                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials"))) %>%

@@

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1)+

@@

#core.did.estimates.strat[,1] <- c("Composite Quality of Care, %","Total Patients, No.","Financial Resilience","Operational Efficiency","Clinical Complexity","Intensity","Medicaid, %","Uninsured, %","Cost Per Patient")

>>>>

strat.temp <- (cbind(core.did.estimates.strat[,1], strat.temp[-1,c(1:2)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "First Shock"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)] %>% 
  rbind((cbind(core.did.estimates.strat[,1], strat.temp[-1,c(5:6)]) %>% 
  data.frame() %>% 
  mutate(Estimate = as.numeric(Estimate), 
         `Std..Error` = as.numeric(Std..Error)) %>% 
  mutate(LB = Estimate - Std..Error * 1.96, 
         UB = Estimate + Std..Error * 1.96) %>% 
  rename(Outcome = V1) %>% 
  mutate(Class = "Multiple Shocks"))[c(1, 2, 3, 4, 11:13, 16:23),c(1,2, 4:6)]) %>% 
  mutate(Measure = ifelse(Outcome %in% c("Qcomp","Total","Altman","logPatsPerStaff","Staff","Closed"), "Overall Metrics", 
                          ifelse(Outcome %in% c("Pct.MCD","Pct.None","Complexity","Intensity"), "Patient Mix", "Financials")))

strat.temp$Outcome <- rep(c("Composite Quality of Care, %", "Total Patients Served, No.","Financial resilience,\nAltman’s Z Score", "Patient-to-Staff Ratio","Average prevalence of\nselect chronic conditions, %","Intensity", "Medicaid, %","Uninsured, %","CostPerPat","Quick Ratio, %","Months of Cash Available", "Revenue-to-Expenses, Ratio %","Liabilities-to-Assets, Ratio %","Staff, No.","Closure, Acquisition or\nloss of FQHC status, %"), 2)

p <- strat.temp  %>% 
  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%

@@

#adding a vertical line at the effect = 0 mark
geom_vline(xintercept=0, color="black", linetype="dashed", alpha= 1) +

@@

p + theme(panel.spacing = unit(1, "lines"),  strip.text = element_text(face = "bold", size = 12))
